---
output: github_document
---

<!-- 
README.md is generated from README.Rmd. 
Please edit that file 
-->

```{r include=FALSE}
# Create .nojekyll file in the /docs folder
file.create('docs/.nojekyll')
# devtools::check() 
# pkgdown::build_site()
# pkgdown::build_articles()
```

baggingbwsel: Bagging bandwidth selection in kernel density and regression estimation
============================================

### `r paste("Version", packageVersion("baggingbwsel"))`

This package implements bagging bandwidth selection methods for the Parzen-Rosenblatt kernel density estimator, and for the Nadaraya-Watson and local polynomial kernel regression estimators. These bandwidth selectors can achieve greater statistical precision than their non-bagged counterparts while being computationally fast. See Barreiro-Ures et al. (2021a) and Barreiro-Ures et al. (2021b).


```{r echo=FALSE, results='asis'}
if ('github_document' == rmarkdown::all_output_formats(knitr::current_input()) && !knitr:::is_html_output()) 
   cat('For more information visit the [web page](https://rubenfcasal.github.io/baggingbwsel) of the package.')
```


Installation
------------

`baggingbwsel` is not yet available from CRAN, but you can install the development version from github with:

```{r install, eval=FALSE}
# install.packages("remotes")
remotes::install_github("rubenfcasal/baggingbwsel")
```

Note also that, as this package requires compilation, Windows users need to have previously installed the appropriate version of [Rtools](https://cran.r-project.org/bin/windows/Rtools/), and OS X users need to have installed [Xcode](https://apps.apple.com/us/app/xcode/id497799835).


Maintainer
----------

[Ruben Fernandez-Casal](https://rubenfcasal.github.io) (Dep. Mathematics, University of A Coruña, Spain). 
Please send comments, error reports or suggestions to [rubenfcasal@gmail.com](mailto:rubenfcasal@gmail.com).


References
----------

* Barreiro-Ures, D., Cao, R., Francisco-Fernández, M., & Hart, J. D. (2021a). [Bagging cross-validated bandwidths with application to big data](https://doi.org/10.1093/biomet/asaa092). *Biometrika*, **108**(4), 981-988, .

* Barreiro-Ures, D., Cao, R., & Francisco-Fernández, M. (2021b). [Bagging cross-validated bandwidth selection in nonparametric regression estimation with applications to large-sized samples](https://arxiv.org/abs/2105.04134). *arXiv preprint*. 
